\documentclass[margin,line]{resume}
\usepackage[utf8]{inputenc} 
%\usepackage[spanish]{babel} 
\usepackage[english]{babel} 

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\begin{document}
\name{Federico G. Mon Trotti \vspace*{.1in}}
\address{Computer Engineer, Software Developer}

\begin{resume}
\vspace{+.2in}
\section{\sc Contact Info}
\vspace{.07in}
\begin{tabular}{@{}p{0.5in}p{2in}}
{\it Phone:} &(+34) 618 128 435 \\
{\it E-mail:} &{ \tt federico.mon@gmail.com}\\
{\it LinkedIn:} &{ \tt http://es.linkedin.com/in/federicomon}\\
\end{tabular}

\vspace{+.2in}
\section{\sc Professional Experience}
{\bf Universidad Complutense de Madrid}, Madrid, Spain

\vspace{-.2cm}
{\bf \em System administrator at ArTeCS investigation group} \hfill
{ Since May 2012
}
\begin{list2}
\vspace*{.06in}
\item {\bf Functions: }{System administration (UNIX and virtualized 
        servers).}
\item {\bf Technologies used: }{Puppet, VMWare ESXi, SSH, LDAP, NFS, Rsync, 
        Bash, Bacula, Nagios, MySQL, Apache, 
        Debian GNU/Linux, Ubuntu GNU/Linux, 
        Solaris 10, Solaris 11.}
\end{list2}

\vspace{+.05in}
{\bf Radmas Technologies}, Madrid, Spain

\vspace{-.2cm}
{\bf \em Web Developer, Backend \& Frontend} \hfill
{ Nov 2011 - Feb 2012
}

\begin{list2}
\vspace*{.06in}
\item {\bf Functions: }{Web development, deployment, testing.}
\item {\bf Technologies used: }{PHP (Symfony), MySQL, HTML5, CSS,
Javascript, JQuery, AJAX, GIT, Apache, Sistemas GNU/Linux de alta
disponibilidad, VMWare ESXi, Heartbeat, PaceMaker.}
\end{list2}

{\bf Universidad Complutense de Madrid}, Madrid, Spain

\vspace{-.2cm}
{\bf \em Internship at Free Software and Open Technologies Office} \hfill
{ Jan - Oct 2011
}
\begin{list2}
\vspace*{.06in}
\item {\bf Functions: }{System administration (UNIX servers \& personal 
computers), teaching, divulgation.}
\item {\bf Technologies used: }{SSH, LDAP, NFS, Rsync, Nagios, PHP
(Drupal), MySQL, Apache, CentOS GNU/Linux, Ubuntu GNU/Linux, Solaris 10.}
\end{list2}


%%\vspace{-.3cm}
%%{\bf \em Becario en el Depto. de Ingeniería del Software e I.A.} \hfill { Octubre -
%%Diciembre 2010}
%%\begin{list2}
%%\vspace*{.05in}
%%\item {\bf Funciones: }{Desarrollo de software.}
%%\item {\bf Technologies used: }{Python, SQLite, sockets.}
%%\end{list2}

{\bf Sinpro Web Solutions}, Eindhoven, The Netherlands

\vspace{-.2cm}
{\bf \em Web developer \& system administrator} \hfill { Oct 2009 -
Jan 2010}
\begin{list2}
\vspace*{.06in}
\item {\bf Functions: }{Web development, web design, deployment, 
system administration.}
\item {\bf Technologies used: }{Gimp, HTML, CSS, PHP (Magento), MySQL,
Apache, Ubuntu GNU/Linux.}
\end{list2}

\vspace{+.2in}
\section{\sc Education}
{\bf Universidad Complutense de Madrid}, Madrid, Spain\\
\vspace*{-.1in}
\begin{list1}
\item[] {\bf \em Computer Science and Engineering }(Jun 2011) 
\begin{list2}
\vspace*{.05in}
\item Master Thesis:  ``Ambiental Intelligence on Mobile Devices'' 
\item Directors:  Manuel Prieto, Marco A. Gómez-Martín
\end{list2}
\end{list1}


{\bf Eindhoven University of Technology}, Eindhoven, The Netherlands\\
\vspace*{-.1in}
\begin{list1}
\item[] {\bf \em Erasmus Program} (Sep 2009 - Jul 2010) 
\end{list1}

\vspace{+.2in}
\section{\sc Software Projects } 
\begin{list1}
\item[] {\bf HD Lorean}
Real-time Backup solution for GNU/Linux.
\vspace*{.05in}
\begin{list2}
\item {\bf Technologies used:} GTK, Python, Xdelta3, Inotify, Sqlite.\\
\end{list2} 

\item[] {\bf Context Manager}
Android application that makes the phone react according to the context 
(time and geolocalization), depending on user-defined rules.
\vspace*{+.03in}
\begin{list2}
\item {\bf Technologies used:} Android SDK, Android APIs: Geolocalization, 
Database, Contacts, Phone states.
\end{list2}
\end{list1}

%%\newpage
\vspace{+.2in}
\section{\sc Technologies} 
\begin{list1}
\item[]{\bf Favorite:}  Python, Django, Flask, Ruby, Rails, Puppet, Javascript, JQuery, HTML5, CSS. 
\item[]{\bf Other Languages \& Frameworks:} Java (J2SE, J2ME, Android), Symfony, PHP, C, C++, SQL, Bash, Prolog, Haskell, Pascal, VHDL, Ensamblador (m68k).
\item[]{\bf Revision Control Systems:} Git, Mercurial, Subversion, Bazaar.
\item[]{\bf System Administration:} Unix/Linux, Solaris, VMWare ESXi.
\end{list1}
%\begin{list2}
%\item {\bf Languajes:} C, C++, Java (J2SE, J2ME, Android), Python,
%Javascript, HTML, SQL, Unix shell scripts, Prolog, Haskell, Pascal, VHDL,
%Ensamblador (m68k).
%\item {\bf Sistemas de Control de Revisiones:} Git, Subversion, Bazaar.
%\item {\bf Sistemas Operativos:} Unix/Linux. 
%\end{list2}

\vspace{+.2in}
\section{\sc Other education } 
\begin{list1}
\item[] {\bf ``Open Source Development for mobile phones" Course} given by Elondra
\item[] {\bf ``Management Skills" Seminar} given by Accenture
\item[] {\bf English Level:} Acredited as B2 (upper intermediate) CEFR
\item[] {\bf Driving License:} B Category
\end{list1}


%\section{\sc Experiencia Personal}
%{\bf Grupo de Usuarios de Linux de la Universidad Complutense de
%Madrid}, Madrid, España
%
%\vspace{-.3cm}
%{\bf \em Socio Fundador, Presidente} \hfill { Marzo 2011 - Actualidad}
%
%
%{\bf Delegación de Alumnos, Facultad de Informática, Universidad Complutense de
%Madrid}, Madrid, España\\
%
%\vspace{-.7cm}
%{\bf \em Representante de Estudiantes} \hfill {Abril 2004 - Abril 2008}\\
%{\bf \em Presidente} \hfill { Abril 2006 - Abril 2008}
%
%{\bf RITSI}, España
%
%\vspace{-.3cm}
%{\bf \em Vocal} \hfill { Noviembre 2005 - Abril 2006}\\
%{\bf \em Presidente} \hfill { April 2006 - Abril 2007}
%
%{\bf ATI}, España
%
%\vspace{-.3cm}
%{\bf \em 2º Vocal en el Capítulo de Madrid} \hfill {%%EN MADRID
%  Nov 2006 - Dic 2009}\\
%
\end{resume}
\end{document}
