\documentclass[helvetica,openbib,totpages]{europecv}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage[a4paper,top=1.27cm,left=1cm,right=1cm,bottom=2cm]{geometry}
\usepackage[english]{babel}
\usepackage{bibentry}
\usepackage{url}

\renewcommand{\ttdefault}{phv} % Uses Helvetica instead of fixed width font

\ecvname{Mon Trotti, Federico Gabriel}
\ecvfootername{Federico G. Mon}
\ecvaddress{Nestares 2, 28045, Madrid, Spain}
\ecvtelephone[+34 618128435]{}
%\ecvfax{(Remove if not relevant)}
\ecvemail{\url{federicomon@gmail.com}}
\ecvnationality{Spanish, Argentinian}
\ecvdateofbirth{24 March 1983}
\ecvgender{Male}
%\ecvpicture[width=2cm]{mypicture}
\ecvfootnote{For more information go to \url{http://europass.cedefop.eu.int}\\
\textcopyright~European Communities, 2003.}

\begin{document}
\selectlanguage{english}


\begin{europecv}
\ecvpersonalinfo[5pt]
\ecvitem{\large\textbf{Desired employment/
Occupational~field}}{\large\textbf{Software Developer, Computer Engineering}}

\ecvsection{Work experience}
\ecvitem{Dates}{Jan 2011 - .}
\ecvitem{Occupation or position held}{ Responsible of the Free Software and Open Technologies
Office (Internship)}
\ecvitem{Main activities and responsibilities}{}
\ecvitem{Name and address of employer}{\ldots}
\ecvitem{Type of business or sector}{\ldots}

\ecvsection{Education and training}

\ecvitem{Dates}{Sep 2003 - Jun 2011}
\ecvitem{Title of qualification awarded}{Computer Science and Engineering}
\ecvitem{Principal subjects/Occupational skills covered}{
Computer Architecture,
Artificial Intelligence,
Hardware Design,
Software Engineering,
Object Oriented Programming, 
Relational Databases,
Computer Networks
}
\ecvitem{Name and type of organization providing education and
training}{Universidad Complutense de Madrid}
%\ecvitem{Level in national or international classification\footnote{If appropriate.}}{\ldots}

\ecvsection{Personal skills and~competences}

\ecvmothertongue[5pt]{Spanish}
%\ecvitem{\large Other language(s)}{}
\ecvlanguageheader{(*)}
\ecvlanguage{English}{\ecvCOne}{\ecvCTwo}{\ecvBTwo}{\ecvCOne}{\ecvCOne}
\ecvlanguagefooter[10pt]{(*)}

\ecvitem[10pt]{\large Social skills and competences}{Replace this text by a description of these competences and indicate where they were acquired (remove if not relevant).}
\ecvitem[10pt]{\large Organisational skills and competences}{Replace this text by a description of these competences and indicate where they were acquired (remove if not relevant).}
\ecvitem[10pt]{\large Technical skills and competences}{Replace this text by a description of these competences and indicate where they were acquired (remove if not relevant).}
\ecvitem[10pt]{\large Computer skills and competences}{Replace this text by a description of these competences and indicate where they were acquired (remove if not relevant).}
\ecvitem[10pt]{\large Artistic skills and competences}{Replace this text by a description of these competences and indicate where they were acquired (remove if not relevant).}
\ecvitem[10pt]{\large Other skills and competences}{Replace this text by a description of these competences and indicate where they were acquired (remove if not relevant).}
\ecvitem{\large Driving licence(s)}{Driving Licence class B.}

\ecvsection{Additional information}
\ecvitem[10pt]{}{Include here any other information that may be relevant, for example contact persons, references, etc. (Remove heading if not relevant).}
\bibliographystyle{plain}
\nobibliography{publications}
\ecvitem{}{\textbf{Publications}}
\ecvitem{}{\bibentry{pub1}}
\ecvitem[10pt]{}{\bibentry{pub2}}
\ecvitem{}{\textbf{Personal interests}}
\ecvitem{}{\ldots}

\ecvsection{Annexes}
\ecvitem{}{List any item attached to the CV}
\end{europecv}


\end{document} 
